Methods for Large Scale Learning to Rank

### 2014-09-29 report/Chapters/CrossBenchmarkComparison.tex
mooie dingen

\subsection{NDCG@3}
Figure \ref{fig:normalised_winning_number_NDCG3} shows the performance of Learning to Rank methods for the \ac{NDCG}@3 metric. Table \ref{tab:raw_data_norm_winnum_NDCG3} in Appendix \ref{app:norm_winnum_NDCG3} provides the raw \ac{NWN} data for the Learning to Rank methods for which \ac{NDCG}@3 evaluation results were available.\\

@@

\subsection{NDCG@5}
Figure \ref{fig:normalised_winning_number_NDCG5} shows the performance of Learning to Rank methods for the \ac{NDCG}@5 metric. Table \ref{tab:raw_data_norm_winnum_NDCG5} in Appendix \ref{app:norm_winnum_NDCG5} provides the raw Normalised Winning Number data for the Learning to Rank methods.\\

@@

\subsection{NDCG@10}
Figure \ref{fig:normalised_winning_number_NDCG10} shows the performance of Learning to Rank methods for the \ac{NDCG}@10 metric. Table \ref{tab:raw_data_norm_winnum_NDCG10} in Appendix \ref{app:norm_winnum_NDCG10} provides the raw Normalised Winning Number data for the Learning to Rank methods.\\

@@

LambdaMART and LambdaNeuralRank score a \ac{NWN} of 1.0 on the \ac{NDCG}@10 comparison. For LambdaNeuralRank these results are again based on AOL dataset measurements. LambdaMART showed the highest \ac{NDCG}@10 performance for the MSLR-WEB10k dataset. The set of algorithms for which there is no other algorithm with both a higher \ac{NWN} and number of data sets evaluated on is partly in agreement with those for the \ac{NDCG}@3 and \ac{NDCG}@5 comparisons: {LARF, LRUF, FSMRank, SmoothRank, ListNet, RankSVM}. SmoothRank and FSMRank were not present in this set for the \ac{NDCG}@3 and \ac{NDCG}@5 comparison, but were close by, as can be seen in Tables \ref{tab:raw_data_norm_winnum_NDCG3} and \ref{tab:raw_data_norm_winnum_NDCG5} in the Appendices. DCMP is not in the set in contrast with the \ac{NDCG}@3 and \ac{NDCG}@5 comparison.

@@

LARF and LRUF score very high \ac{NWN} scores, but based on only relatively few data sets, just as in the \ac{NDCG}-comparisons. Notable is that SmoothRank and ListNet, which showed both high accuracy and high certainty on all \ac{NDCG}-comparisons, are not within the best performing methods in the \ac{MAP}-comparison. A deeper look in the raw data Tables \ref{tab:raw_data_norm_winnum_NDCG3} to \ref{tab:raw_data_norm_winnum_map} in Appendices \ref{app:norm_winnum_NDCG3} to \ref{app:norm_winnum_map} shows that LAC-MR-OR is evaluated on many more data sets for \ac{MAP} compared to \ac{NDCG}, which resulted in LAC-MR-OR obtaining equal certainty to ListNet with a higher \ac{NWN}. SmoothRank performed a \ac{NWN} of around 0.53 over 7 data sets, which is still good in both certainty and accuracy, but not among the top methods. RE-QR is one of the best performers in the \ac{MAP}-comparison with a reasonable amount of benchmark evaluations. No reported \ac{NDCG} performance was found in the literature study for RE-QR. There is a lot of certainty on the accuracy of RankBoost and Rank\ac{SVM} as both models are evaluated on the majority of data sets included in the comparison for the \ac{MAP}-metric, but given their \ac{NWN} it can said that both methods are not within the top performing Learning to Rank methods.

@@

Our comparison regarded evaluation results on \ac{NDCG}@{3, 5, 10} and \ac{MAP}. By making the decision to include \ac{NDCG} at three cut-off points and only a single \ac{MAP} entry, we implicitly attain a higher weight for \ac{NDCG} compared to \ac{MAP} on an analysis that combines all measurements on the four metrics. This implicit weighting could be regarded as arbitrary, but the number of algorithm evaluation results gained by this makes it a pragmatic approach. Note that another implicit weighting lies in the paper dimension. Hence, the higher number of evaluation results specified in a paper, the higher the influence of this paper on the outcome of the analysis. This implicit weighting is not harmful to the validity of our comparison, as papers with a large number of evaluation results are more valuable than papers with a few evaluation results. In addition, papers with a high number of evaluation results are not expected to be less reliable than papers with fewer evaluation results.

>>>>

\subsection{NDCG@3}
Figure \ref{fig:normalised_winning_number_NDCG3} shows the performance of Learning to Rank methods for the \ac{NDCG}@3 metric. Table \ref{tab:raw_data_norm_winnum_ndcg3} in Appendix \ref{app:norm_winnum_ndcg3} provides the raw \ac{NWN} data for the Learning to Rank methods for which \ac{NDCG}@3 evaluation results were available.\\

@@

\subsection{NDCG@5}
Figure \ref{fig:normalised_winning_number_NDCG5} shows the performance of Learning to Rank methods for the \ac{NDCG}@5 metric. Table \ref{tab:raw_data_norm_winnum_ndcg5} in Appendix \ref{app:norm_winnum_ndcg5} provides the raw Normalised Winning Number data for the Learning to Rank methods.\\

@@

\subsection{NDCG@10}
Figure \ref{fig:normalised_winning_number_NDCG10} shows the performance of Learning to Rank methods for the \ac{NDCG}@10 metric. Table \ref{tab:raw_data_norm_winnum_ndcg10} in Appendix \ref{app:norm_winnum_ndcg10} provides the raw Normalised Winning Number data for the Learning to Rank methods.\\

@@

LambdaMART and LambdaNeuralRank score a \ac{NWN} of 1.0 on the \ac{NDCG}@10 comparison. For LambdaNeuralRank these results are again based on AOL dataset measurements. LambdaMART showed the highest \ac{NDCG}@10 performance for the MSLR-WEB10k dataset. The set of algorithms for which there is no other algorithm with both a higher \ac{NWN} and number of data sets evaluated on is partly in agreement with those for the \ac{NDCG}@3 and \ac{NDCG}@5 comparisons: {LARF, LRUF, FSMRank, SmoothRank, ListNet, RankSVM}. SmoothRank and FSMRank were not present in this set for the \ac{NDCG}@3 and \ac{NDCG}@5 comparison, but were close by, as can be seen in Tables \ref{tab:raw_data_norm_winnum_ndcg3} and \ref{tab:raw_data_norm_winnum_ndcg5} in the Appendices. DCMP is not in the set in contrast with the \ac{NDCG}@3 and \ac{NDCG}@5 comparison.

@@

LARF and LRUF score very high \ac{NWN} scores, but based on only relatively few data sets, just as in the \ac{NDCG}-comparisons. Notable is that SmoothRank and ListNet, which showed both high accuracy and high certainty on all \ac{NDCG}-comparisons, are not within the best performing methods in the \ac{MAP}-comparison. A deeper look in the raw data Tables \ref{tab:raw_data_norm_winnum_ndcg3} to \ref{tab:raw_data_norm_winnum_map} in Appendices \ref{app:norm_winnum_ndcg3} to \ref{app:norm_winnum_map} shows that LAC-MR-OR is evaluated on many more data sets for \ac{MAP} compared to \ac{NDCG}, which resulted in LAC-MR-OR obtaining equal certainty to ListNet with a higher \ac{NWN}. SmoothRank performed a \ac{NWN} of around 0.53 over 7 data sets, which is still good in both certainty and accuracy, but not among the top methods. RE-QR is one of the best performers in the \ac{MAP}-comparison with a reasonable amount of benchmark evaluations. No reported \ac{NDCG} performance was found in the literature study for RE-QR. There is a lot of certainty on the accuracy of RankBoost and Rank\ac{SVM} as both models are evaluated on the majority of data sets included in the comparison for the \ac{MAP}-metric, but given their \ac{NWN} it can said that both methods are not within the top performing Learning to Rank methods.

@@

Our comparison regarded evaluation results on \ac{NDCG}@$\{3,5,10\}$ and \ac{MAP}. By making the decision to include \ac{NDCG} at three cut-off points and only a single \ac{MAP} entry, we implicitly attain a higher weight for \ac{NDCG} compared to \ac{MAP} on an analysis that combines all measurements on the four metrics. This implicit weighting could be regarded as arbitrary, but the number of algorithm evaluation results gained by this makes it a pragmatic approach. Note that another implicit weighting lies in the paper dimension. Hence, the higher number of evaluation results specified in a paper, the higher the influence of this paper on the outcome of the analysis. This implicit weighting is not harmful to the validity of our comparison, as papers with a large number of evaluation results are more valuable than papers with a few evaluation results. In addition, papers with a high number of evaluation results are not expected to be less reliable than papers with fewer evaluation results.

### 2014-09-29 report/Chapters/Future.tex
mooie dingen

\section{Computing models}
We explored the possibilities of Hadoop MapReduce for distributed computation of Learning to Rank training algorithms. Hadoop, since the introduction of Hadoop YARN in Hadoop 2.0, offers integration with other distributed computing models, including Dryad \cite{Isard2007}, Spark \cite{Zaharia2010}, Storm \cite{Aniello2013} and MPI. Of these distributed programming models, Spark is particularly promising, since Shukla et al. \cite{Shukla2012} already showed that it is able to speed-up the ListNet training procedure with much lower job scheduling overhead than that we found for MapReduce. For the newly supported programming models in Hadoop, it holds that they lack the critical mass as the distributed programming model of choice. This lack of a critical mass results in higher integration costs and less available support. The integration of new programming model into the Hadoop YARN framework is a step in the good direction to alleviate the integration cost of these programming models, but does not yet completely eliminate the problem. Cloud-based Hadoop services like Microsoft HDInsight and Amazon Elastic MapReduce.

\section{Learning to Rank algorithms}

>>>>

\section{Distributed Computing Models}
We explored the possibilities of Hadoop MapReduce for distributed computation of Learning to Rank training algorithms. Hadoop, since the introduction of Hadoop YARN in Hadoop 2.0, offers integration with other distributed computing models, including Dryad \cite{Isard2007}, Spark \cite{Zaharia2010}, Storm \cite{Aniello2013} and MPI. Of these distributed programming models, Spark is particularly promising, since Shukla et al. \cite{Shukla2012} already showed that it is able to speed-up the ListNet training procedure with much lower job scheduling overhead than that we found for MapReduce. For the newly supported programming models in Hadoop, it holds that they lack the critical mass as the distributed programming model of choice. This lack of a critical mass results in higher integration costs and less available support. The integration of new programming model into the Hadoop YARN framework is a step in the good direction to alleviate the integration cost of these programming models, but does not yet completely eliminate the problem. Cloud-based Hadoop services like Microsoft HDInsight and Amazon Elastic MapReduce.

\section{Learning to Rank Algorithms}
As an answer to the first research question of this thesis, we found five Learning to Rank methods for it holds that no other algorithm produced more accurate rankings with a higher degree of certainty of ranking accuracy. These algorithms were, from highest ranking accuracy / lowest certainty to lowest ranking accuracy / highest certainty: ListNet, SmoothRank, FenchelRank, FSMRank and LRUF. In this thesis we explored the speed-up characteristics of ListNet on Hadoop MapReduce. The speed-up characteristics of SmoothRank, FenchelRank, FSMRank and LRUF are using the MapReduce computing model are still to be explored.

\section{Optimisation Algorithms}
